
%% AUTHOR:  GERARDO TORRES
%% URl:     HTTPS://GITHUB.COM/GTR/RES
%%          HTTPS://GERARDO.TO/

\documentclass[letterpaper,10pt]{article}

%% PACKAGES

\nofiles
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage[empty]{fullpage}
\usepackage{geometry}
\usepackage{multirow}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{array}
% \usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{colortbl}
\usepackage{enumitem}
\usepackage{calc}

%% MARGINS %%

\usepackage{graphicx}
\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

\geometry{
    letterpaper,
    total={182mm,310mm},
    left=15mm,
    top=11mm,
    right=-15mm
}

\raggedright
% \setcounter{secnumdepth}{0}

%% CUSTOM COMMANDS %%

% Color on lines and name
\definecolor{burgundy}{rgb}{0,0,0}
\definecolor{light-grey}{rgb}{0.4,0.4,0.4}

% Command for displaying organizations (schools & employers)
\newcommand{\organization}[4]{
    \vspace{1.5pt}
    \textbf{#1} \hfill{\emph{#2}} \\
    \emph{#3} \hfill{#4} \\
    \vspace{3pt}
}

\newcommand{\toolsused}[1]{
    \vspace{1.5pt}
    \emph{#1}\\
    \vspace{3pt}
}


% Command for displaying projects
\newcommand{\project}[2]{
    \textbf{#1} -- \emph{#2} \\
}

\newcommand{\pro}[4]{
    \item \href{#2}{\textbf{#1}} -- {#3} \textbf{\textit{#4}}
    % \vspace{1pt}
}

% Command for displaying skills table
\newcommand{\skills}[4]{
    \vspace{-2pt}
    \ \ \ \ \ \ \ \ \ \ \ 
    \begin{tabular}{r!{\color{burgundy}\vrule}l}
          Programming & #1 \\
          Frameworks/Libraries & #2 \\
          Databases & #3 \\
          Tools & #4
    \end{tabular}
    \vspace{4pt}
}


% Command for displaying individual awards & activity bullets
\newcommand{\activity}[2]{
    \item #1 \hfill{\emph{#2}}
}

% Command for the beginning of bullets in work exp and projects
\newcommand{\bulletsBegin}{
    \vspace{1pt}
    \begin{minipage}{17.6cm}
    \begin{itemize}[leftmargin=0.6cm]
    \setlength\itemsep{-0.1em}
}

% Command for the end of bullets in work exp and projects
\newcommand{\bulletsEnd}{
    \end{itemize}\vspace{0pt}
    \end{minipage}
}

% Command for the beginning of bullets in work exp and projects
\newcommand{\bulletsBeginn}{
    \vspace{1pt}
    \begin{minipage}{18cm} 
    \begin{itemize}[leftmargin=0.6cm]
    % \setlength\itemsep{-0.018em}
}

% Command for the end of bullets in work exp and projects
\newcommand{\bulletsEndd}{
    \end{itemize}\vspace{0pt}
    \end{minipage}
}

% Command for email
\newcommand{\myEmail}[1]{
    \href{mailto:divyanss@usc.edu}{#1}
    \ |
}

% Command for phone
\newcommand{\myPhone}[1]{
    {#1}
    \ |
}

% Command for personal website
\newcommand{\mySite}[1]{
    \href{https://linkedin.com/in/divyanshi26}{#1}
    \ |
}

% Command for github profile
\newcommand{\myGitHub}[1]{
    \href{https://github.com/divyanshi26}{#1}
}

% Command for displaying name and Contact info
\newcommand{\myName}[5]{
    \begin{center}
        {\huge{\color{burgundy}\scshape{#1}}} \\
        \vspace{6pt}
        \myEmail{#2}
        \myPhone{#3}
        \mySite{#4}
        \myGitHub{#5}
    \end{center}
    \vspace{-4pt}
}

% Title formatting for each section on resume
\titleformat{\section}{
	\vspace{-16pt}\color{burgundy}\scshape\raggedright\large
	}{}{0em}{}[\titlerule\vspace{-1pt}]

%% DOCUMENT 

\begin{document}

    %% HEADING --------------------
    \myName{Divyanshi Sharma}{divyanss@usc.edu}{551-502-4023}{linkedin.com/in/divyanshi26}{github.com/divyanshi26}

    %% EDUCATION --------------------
    \section{Education}
        
    \organization{Master of Science in Computer Science}{2020}
        {University of Southern California, Viterbi School of Engineering}{GPA: 3.60/4.00}
        % \vspace{4pt}

	\organization{Bachelor of Science in Computer Science and Engineering}{2017}
        {Jaypee University of Engineering and Technology}{GPA: 8.90/10.00}
        \vspace{5pt}

    %% WORK EXPERIENCE --------------------
    % \vspace{5pt}
    \section{Work Experience}

        \organization{Kaspect Labs}{May 2019 - Present}
        {Research Intern}{Los Angeles, CA}
        \bulletsBegin
            \item Served as team lead with two masters-level developers in developing a prototype for a gamified Virtual Reality device quantifying upper extremity range-of-motion and neuromuscular coordination in the paediatric outpatient setting.
            \item Programmed a reliable and fault-tolerant real-time bidirectional connection between Unity and JavaScript via a RESTful API.
            \item Designed an in-game Principal Component Analysis (PCA) on the Patient’s motion, leveraging the results to create new patient-appropriate tasks.
        \bulletsEnd
        \vspace{-3pt}
        \toolsused{Tools: Unity3D, Python, C\#, Flask, Azure, JavaScript, ZeroMQ}

        \organization{Freelicious}{Jun 2019 - Present}
        {Frontend Developer}{Los Angeles, CA}
        \bulletsBegin
            \item Heading the Frontend Mobile Development Team, assigning weekly tasks, and coordinating with the Backend Team for integration.
            \item Collecting and translating design team's UX wireframes and mock-ups into responsive, interactive features into a hybrid mobile application, using Angular with Ionic, HTML5, CSS3, and JavaScript.
        \bulletsEnd

        \organization{Wipro Technologies Ltd.}{Oct 2017 - Jul 2018}
        {Project Engineer}{Hyderabad, India}
        \bulletsBegin
            \item Programmed and enhanced the frontend of a hybrid mobile application tracking requests submitted for collection of assets and provided a real-time dashboard to monitor progress and display statistics.
            \item Delivered UI fixes and debugged the source code in a ticket managing application developed using .NET and AngularJS.
            \item \textbf{\textit{Tools: Angular, Ionic,Bootstrap}}
        \bulletsEnd

    %% PROJECTS --------------------
    \section{Projects}

        % \vspace{1pt}
    
        \bulletsBegin
            \vspace{-3pt}
        \pro{Yelp Rating Predictor (Foundations and Applications of Data Mining)}
            {https://github.com/example/project}
            {Predicted yelp review ratings using an ensemble of collaborative filtering techniques, reducing the RMSE from 1.18 to 0.99.}
            {Python, Apache Spark, scikit-surprise.}
        \pro{Part of Speech Tagger (Applied Natural Language Processing)}
            {https://github.com/example/project}
            {Implemented a Part-of-Speech tagger from scratch using Hidden Markov Models (HMM) and the Viterbi Algorithm to achieved an F1 score of over 96\%, using Italian and Japanese datasets.}
            {Python.}
        
        % \vspace{-1pt}
        \bulletsEnd

    %% SKILLS --------------------
    \section{Skills}
    
    \skills
        {C++, Python, SQL, C\#, JavaScript, Java}  % Programming
        {Flask, Angular, Ionic, ZeroMQ, Apache Spark, Django, numpy, scikit-learn}  % Frameworks/Libraries
        {MySQL, Oracle, SQL Server, PostGIS}  % Databases
        {Git, Unity3D, Azure}  % Tools

    %% AWARDS --------------------
    
    \section{Leadership \& Awards}

    \bulletsBegin
        \activity{Viterbi Career Ambassador, Viterbi Career Connections.}{Jan 2019 - May 2020}
        \vspace{-4pt}
        \activity{Course Producer, CSCI 544 Applied Natural Language Processing, University of Southern California.}{Jan 2020 - May 2020}
        \vspace{-4pt}
        \activity{Best "Hack for Good", AthenaHacks, University of Southern California.}{Apr 2019}
    \bulletsEnd

    % \vspace{3pt}
    % \color{light-grey}
    % R\'esum\'e \hfill{Updated: July 2019}

\end{document}
